Benchmarking FDR Methods - Summarizing Simulation Results

### 2017-11-03 datasets/simulations/analysis-03-plot-tsim-summaries.Rmd
Fix typos in t-test sim summary plots

In this analysis, we look at summarizing the results for the various simulation settings considered under the two-sample t-test setting. Each simulation included 20,000 two-sample t-tests performed over a variable number of null (group difference 0) and alternative (group difference > 0) datasets. Different simulation settings were considered to evaluate the impact of varying group sample sizes, effect sizes, effect size distributions, proportions of null hypotheses, and presence or absence of an informative covariate. More details on the simulation settings considered are included in the header of the `tsim-core-settings.R` script. Each simulation setting was replicated 100 times.

In a previous analysis (`analysis-01-plot.Rmd`), each simulation setting was considered and plotted separately with performance metrics reported over a range of FDR ("alpha") thresholds. However, since the total number of settings considered is quite large, processing and interpreting these results was both cumbersome and difficult. To get a higher-level picture of the simulation results, here we consider a single FDR threshold, `alpha = 0.05` and plot performance metrics for each method within sets of related simulation settings. Plots for FPR and "rejectprop" (rejection proportion) include blue horizontal lines at the expected FDR level (`0.05`) and proportion of alternative hypotheses (`1 - pi0`), respectively.

@@

<!-- ######################################################################## -->
### SE as Informative Covariate

@@

<!-- ######################################################################## -->
### Boca-Leek Style Informative Covariate

>>>>

In this analysis, we look at summarizing the results for the various simulation settings considered under the two-sample t-test setup. Each simulation included 20,000 two-sample t-tests performed over a variable number of null (group difference 0) and alternative (group difference > 0) datasets. Different simulation settings were considered to evaluate the impact of varying sample sizes, effect sizes, effect size distributions, proportions of null hypotheses, and presence or absence of an informative covariate. More details on the simulation settings considered are included in the header of the `tsim-core-settings.R` script. Each setting was replicated 100 times.

In a previous analysis (`analysis-01-plot.Rmd`), each simulation setting was considered and plotted separately with performance metrics reported over a range of FDR ("alpha") thresholds. However, since the total number of settings considered is quite large, processing and interpreting these results was both cumbersome and difficult. To get a higher-level picture of the simulation results, here we consider a single FDR threshold, `alpha = 0.05`, and plot performance metrics across settings for each method. Plots for FPR and "rejectprop" (rejection proportion) include blue horizontal lines at the expected FDR level (`0.05`) and proportion of alternative hypotheses (`1 - pi0`), respectively.

@@

<!-- ######################################################################## -->
### SE as Covariate

@@

<!-- ######################################################################## -->
### Boca-Leek Style Covariate
